### 2017-07-12 paper/jfp-submission/evaluation.tex
oops

\subsection{Quantitative Evaluation of Witness Utility}
\label{sec:user-study}
% Finally, to test the explanatory power of our jump-compressed traces, we
% ran a user study (IRB \#2014009900) at the University of Virginia (UVA).
% %
% We included four problems in an exam in the Spring session of UVA's
% undergraduate Programming Languages course (CS 4501).
% %
% We presented the 60 students in the course with ill-typed \ocaml\
% programs and asked them to
% %
% (1) \emph{explain} the type error, and
% %
% (2) \emph{fix} the type error.
% %
% For each problem the student was given the ill-typed program and
% either \ocaml's error message or \toolname's jump-compressed trace.
%
We assigned four problems to the 60 students in the course: the
@sumList@, \hbox{@digitsOfInt@,} and @wwhile@ programs from
\S~\ref{sec:advantage-traces}, as well as the following @append@ program
%
\begin{ecode}
  let append x l =
    match x with
    | []   -> l
    | h::t -> h :: t :: l
\end{ecode}
%
which triggers an occurs-check error on line 4.
%
For each problem the students were given the ill-typed program and
either \ocaml's error or \toolname's jump-compressed trace;
the full user study is available in \S~\ref{sec:user-study}.
%
Due to the nature of an in-class exam, not every student answered every
question; we received between 13 and 28 (out of a possible 30) responses
for each problem-tool pair.

>>>>

\subsection{Quantitative Evaluation of Witness Utility}
\label{sec:user-study}
% Finally, to test the explanatory power of our jump-compressed traces, we
% ran a user study (IRB \#2014009900) at the University of Virginia (UVA).
% %
% We included four problems in an exam in the Spring session of UVA's
% undergraduate Programming Languages course (CS 4501).
% %
% We presented the 60 students in the course with ill-typed \ocaml\
% programs and asked them to
% %
% (1) \emph{explain} the type error, and
% %
% (2) \emph{fix} the type error.
% %
% For each problem the student was given the ill-typed program and
% either \ocaml's error message or \toolname's jump-compressed trace.
%
We assigned four problems to the 60 students in the course: the
@sumList@, \hbox{@digitsOfInt@,} and @wwhile@ programs from
\S~\ref{sec:advantage-traces}, as well as the following @append@ program
%
\begin{ecode}
  let append x l =
    match x with
    | []   -> l
    | h::t -> h :: t :: l
\end{ecode}
%
which triggers an occurs-check error on line 4.
%
For each problem the students were given the ill-typed program and
either \ocaml's error or \toolname's jump-compressed trace;
the full user study is available in Appendix~\ref{sec:user-study-exams}.
%
Due to the nature of an in-class exam, not every student answered every
question; we received between 13 and 28 (out of a possible 30) responses
for each problem-tool pair.
